%!TEX TS-program = xelatex
\documentclass[print]{friggeri-cv}

\begin{document}
\header{Andrew}{Braunstein}
       {Software Engineer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
  34 Belmont Drive West
  Roslyn Hts., NY 11577
  ~
  (516)526-5739
  ~
  \href{mailto:awbraunstein@gmail.com}{awbraunstein@gmail.com}
  \href{http://andrewbraunstein.com}{andrewbraunstein.com}
  \href{http://github.com/awbraunstein}{github.com/awbraunstein}
  \section{languages}
  Ruby, Javascript, CoffeeScript, C, Python, Java, C++, Bash
  \section{frameworks}
  Rails, Sinatra, Flask, Expressjs, Android
  \section{tools}
  Emacs, Eclipse, QtCreator, Visual Studio
\end{aside}

\section{education}

\begin{entrylist}
  \entry
    {2009–2012}
    {University of Pennsylvania}
    {Philadelphia, PA}
    {BSE in Computer Science \\
    Expected Graduation: May 2013}
\end{entrylist}

\section{experience}

\begin{entrylist}
  \entry
    {05/12-08/12}
    {Vistar Media}
    {Philadelphia PA}
    {Software Engineer Intern \\
      \emph{Rewrote serverside form validations, replacing wtforms \\ 
        Built new clientside visualizations using d3.js }}
  \entry
    {09/11-05/12}
    {University Of Pennsylvania}
    {Philadelphia, PA}
    {Teaching Assistant \\
      \emph{Taught labs for Programming Languages I. \\ 
        Held office hours and did code reviews.}}
  \entry
    {06/11–08/11}
    {Gobbler}
    {Hollywood, CA}
    {Software Engineer Intern \\ 
      \emph{Developed an internal marketing tool in Ruby on Rails. \\ 
      Built a forum scraper that parses phpBB and vBulletin forums}}

\end{entrylist}

\section{projects}

\begin{entrylist}
  \entry
  {2012}
  {\href{http://andrewbraunstein.com:3000}{js-compute}}
  {CoffeeScript, Node.js}
  {js-compute is a distributed JavaScript cloud-computing platform. \\
    Using web workers, js-compute can harness the power of the user's
    browser to compute distributed tasks}
  \entry
  {2012}
  {\href{http://rdtripp.in}{rdtripp.in}}
  {Javascript, Python}
  {3rd place (\$1000) out of 42 teams at PennApps 2012 Spring
    Hackathon \\ 
    A webapp that finds your facebook friends that live along a
    route. \\
    Uses backbone.js, googlemaps API, and mongoDB.}
  \entry
  {2011}
  {\href{http://andrewbraunstein.com/settlethis.html}{Let's Settle This}}
  {Java, Android}
  {Android app that allows you to settle petty arguments with
    friends quickly and easily. \\ 
    Uses Venmo mobile payment API, Wolfram Alpha search API, and Bump mobile to mobile data transfer API.}
  \entry
  {2011}
  {Wii Conductor}
  {Java, AppleScript}
  {Written at TechCrunch’s Disrupt Hackathon 2011, this program allows
    the user to control the tempo and volume of a song playing in
    GarageBand by using a Wiimote to conduct the music.}
\end{entrylist}

\section{interests}

\begin{entrylist}
  \entry
  {Founder, Emacs club on campus}{}{}{}
  \entry
  {Board Member, UPenn Ski and Snowboard Team}{}{}{}
  \entry
  {Board Member, Dining Philosophers (UPenn Computer Science Club)}{}{}{}
  
\end{entrylist}

\end{document}
